Clustering: A pipeline to analyse time-course gene expression data

### 2019-02-22 scripts/03_clustering.Rmd
ENH Can now keep all the DE genes above the lfc threshold

# Clustering
filter_genes = TRUE
n_genes_to_keep = 5000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

	# Then rank by fisher's p-value and take max the number of genes of
	# interest
	# Filter out q-values for the pvalues table
	pval_col_to_keep = colnames(pvalues)[grepl("-pval", colnames(pvalues))]
	pvalues = pvalues[, pval_col_to_keep]
	fishers_pval = moanin:::fisher_method(pvalues)
    } else {
	genes_to_keep = names(pvalues)
    }
    genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}

@@

kmeans_clusters = moanin:::splines_kmeans(
    y, meta, n_clusters=20,
    random_seed=42,
    degrees_of_freedom=df)

>>>>

###############################################################################
# Clustering

# Whether to filter genes
filter_genes = TRUE
keep_all_significant = TRUE
n_genes_to_keep = 5000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

	# Then rank by fisher's p-value and take max the number of genes of
	# interest
	# Filter out q-values for the pvalues table
	pval_col_to_keep = colnames(pvalues)[grepl("-pval", colnames(pvalues))]
	pvalues = pvalues[, pval_col_to_keep]
	fishers_pval = moanin:::fisher_method(pvalues)
    } else {
	genes_to_keep = names(pvalues)
    }

    if(keep_all_significant){
	genes_to_keep = names(fishers_pval[fishers_pval < 0.05])
    }else{
        genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
    }
    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}

@@

kmeans_clusters = moanin:::splines_kmeans(
    y, meta, n_clusters=20,
    random_seed=42,
    n_init=20,
    degrees_of_freedom=df)
